Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-04-25 paper.Rmd
first batch of edits
I've edited the first part of the paper and added a few comments - search !!! to jump directly to them.

## Final tutorials

The final tutorals are available for download at <https://github.com/ABMArchaeologists/ABMA_tutorials> and are citeable [@rocks-macqueen2024]. The set of developed tutorials consists of the following tutorials:

@@

Each tutorials consists of a different number of lessons that guide the learner in a self-pace manner through the lessons.

In the first tutorial the user will learn what simulations and agent-based models are and how they can help in archaeological research. This tutorial consists of 4 lessons. The first two lessons introduce the learner to simulation in general and Agent-Based Modelling in specific. Various concepts related to ABM are introduced and the first concepts within NetLogo are explained. The third lesson aims to explain how ABMs are used in archaeological research. The final lesson introduces the learner to the NetLogo Interface and the difference between the Interactive and Authoring mode. This tutorial build a foundation for working in NetLogo and with ABM. All activity stays within the intermediate level, although higher levels might be touched upon.

>>>>

## ABM tutorials

The final set of ABMA tutorals are available for download at <https://github.com/ABMArchaeologists/ABMA_tutorials> and are citeable [@rocks-macqueen2024]. The set of developed tutorials consists of the following tutorials:

@@

Each tutorials consists of a number of individual lessons, each of which guides the learner in a self-pace manner through an increasingly challenging set of exercises that build the skills and knowledge necessary to become a confident agent-based modeller.

In the first tutorial the user learn what simulations and agent-based models are and how they can help in archaeological research. This tutorial consists of 4 lessons. The first two lessons introduce the learner to simulation in general and Agent-Based Modelling in specific. Various concepts related to ABM are introduced and the first concepts within NetLogo are explained. The third lesson aims to explain how ABMs are used in archaeological research. The final lesson introduces the learner to the NetLogo Interface and the difference between the Interactive and Authoring mode. This tutorial build a foundation for working in NetLogo and with ABM. All activity stays within the intermediate level, although higher levels might be touched upon.
